%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience \& Volunteer Work}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Business Analyst Intern (Attachment)} % Job title
    {Sony} % Organization
    {May. 2022 - Aug. 2022} % Date(s)
    {} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participate in Harmonization / Business Process Reengineering activities within Sony companies geared towards the system implementation of new global SAP system.}
        \item {Participate in global UAT discussions with utilization of ALM (Application Lifecycle Management)}
        \item {Acquire knowledge in designing PowerApps, Power Automation and PowerBI}
        \item {Identify UI/UX problems and propose interface improvements}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {UI/UX feedback Volunteer (Voluntary)} % Job title
    {The Hidden Good (THG)} % Organization
    {Dec. 2021 - Mar. 2022} % Date(s)
    {} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Map out business processes to identify bottlenecks and propose IT solutions}
        \item {Develop user-centered designs from business requirements and user feedback}
        \item {Generating user flows, wireframes, and prototypes}
        \item {Identifying and troubleshooting UX problems}
        \item{Using customer feedback, usage metrics, and usability findings into design to enhance user experience. This will assist in developing the Human Machine Interface (HMI)}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {IT Consultant Intern (Attachment)} % Job title
    {Civil Aviation Authority of Singapore (CAAS) - Civil Aviation Medical Board (CAMB)} % Organization
    {May. 2021 - Aug. 2021} % Date(s)
    {} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Undergo a project to enhance the Electronic Licensing Medical Records System (ELMeRS) which is an end-to-end service platform that supports the business processes of the medical certification regime.}
        \item {Understanding the medical fitness certification requirements, business processes and oversight approach in order to ensure the system meets the needs of the user.}
        \item {Understand approach to digitalization, e-services and cybersecurity challenges for an electronic medical records system in a closed loop \\ environment which requires compliance to IM8.}
        \item {Study and propose solutions for functional bugs experienced by the user interface}
        \item {Analyze quality of data acquired and issues to derive the factors that determines the system performance and usability}
        \item {Understand the importance of a Business Continuity Planning (BCP) and its importance in Singapore’s aviation safety framework}
        \item {Appreciate government policies and policy strategies on a global level while participating as a member of International Civil Aviation \\ Organization (ICAO) }
        \item {Propose innovative ideas using both AI and Automation processes in preparation for the next generation ELMeRS.}
        \item {Work closely with developers and contractors through Focus Group Discussion (FGD) in future proofing ELMeRS}
        \item {Assisted in the generation of Designated Medical Examiner (DME) audit statistics which is to be used in Universal Safety Oversight Safety Audit (USOAP) international audit to display CAMB’s oversight process and compliance}
        \item {Implement VBA and Macro methodologies to improve accuracy and efficiency for the purpose of mining quality data. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Programmer Intern (Attachment)} % Job title
    {A*STAR - Data Storage Institute (DSI)} % Organization
    {Sep. 2017 - Feb. 2018} % Date(s)
    {} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Graphic User Interfaces (GUIs) using Python software to aid A*STAR researchers in the processing of sophisticated data utilized for experimental outputs (e.g., microscopic images)}
        \item {Develop a customized tool using Python Programming Language to perform image processing for Skyrmions (Particle Theory). The processing of data through image rendering is a sophisticated process relying on complex mathematical models using the Gaussian Function}
        \item{Develop a customized tool using Python Programming Language to convert data files to Spectra Image by relying on data points and sorting algorithms, numerical data is hence converting to a readable and relatable chart image for further study and references which would be useful for conclusion of findings/ studies.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Assistant Engineer (Vacation Job Stint) } % Job title
    {Auresys PTE LTD} % Organization
    {Mar. 2015 - Mar. 2015} % Date(s)
    {} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Carry out studies on mechanical components to improve the vending machine features}
        \item {Carry out on-site troubleshooting works which includes hardware and software rectification to operationalize the machine}
        \item{Understand the customer’s pain points and challenges to develop new features to be included in Auresys product offering which was subsequently adopted by the company. }
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
